\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-16 icse/related.tex
Revised intro & overview
Updated images
Written related work for parsers

\section{Related Work}

Our technique is closely related by these fields: Parser generation, Automatic model generation, and Formal semantics of JavaScript.
\subsection{Parser Generation}
\begin{itemize}
  \item Packrat parsing:: simple, powerful, lazy, linear time, functional pearl (ICFP'02)~\cite{packrat}
    % left recursion 잘 안됨 / memoization으로 memory가 엄청 커짐
    % GLL - follow가 아닌 prediction으로 사용함 / 이 방법을 적용하면 중간중간 발생하는 nondeterministic한 경우를 모두 keeping해야됨.
    % context-sensitive token이기에 미리 parsing을 한 token이 존재하지 않기 때문에 그 다음 token이 뭔지 알 수 없어서 prediction도 하지 못함
\end{itemize}

\subsection{Automatic Model Generation}
There is similar problems in many fields. Not only language semantics, many specification is not constructed formally, so many researches are trying to
extract formal semantics of target specification. To reduce manual efforts to get models of target system, there are few studies about automatic generation of
formal semantics from specification. \cite{javadoc} is closely related work of ours, which uses Javadoc comments of target API function with NLP techniques and various
heuristic methods, to generate java code which correctly models target. They produces several candidate codes, and test their codes with actual implementation of API functions
to find correct modeling. Unlike their approaches, we provides specification translation assistant to support future language update, and to provide correct meaning of specification, which also can applicable when
testing for each primitive is unavailable so we cannot decide correct semantics automatically.

@@

\subsection{Formal Semantics of JavaScript}

>>>>

\section{Related Work}\label{sec:related}

Our technique is closely related by these fields: parser generation, automatic model generation, and formal semantics of JavaScript.

From Packrat parsing~\cite{packrat} with parsing expression grammars (PEG (PEG))~\cite{peg},
the recursive-descent parsers with backtracking supports linear-time parsing.
However, it suffers from the fundamental problem of ordered choices;
\( ab \) is silently unmatched in \( a \mid ab \) quirk.
The Generalized LL (GLL) parsing~\cite{gll} is basically recursive-descent with backtracking
but it could support general context-free grammars (CFG) even including ambiguous grammars.
However, it takes \( O(n^3) \) parsing time when the input size is \( n \) in worst cases.
While it could be reduced into almost linear time on most real grammars,
it should keep all intermediate possible parsing results during parsing mechanisms.
Unlike GLL parsing, our lookahead parsing is not applicable into general context-free grammar.
However, we experimentally show that JavaScript parsers could be generated via lookahead parsers.
Lookahead parsers take \( O(kn) \) where \( n \) is the length of inputs and \( k \)
is the number of tokens. In JavaScript parser, it has only constant number of tokens
thus the generated JavaScript parsers with lookahead parsers take linear time.

There is similar problems in many fields. Not only language semantics, many specification is not constructed formally, so many researches are trying to
extract formal semantics of target specification. To reduce manual efforts to get models of target system, there are few studies about automatic generation of
formal semantics from specification. \cite{javadoc} is closely related work of ours, which uses Javadoc comments of target API function with NLP techniques and various
heuristic methods, to generate java code which correctly models target. They produces several candidate codes, and test their codes with actual implementation of API functions
to find correct modeling. Unlike their approaches, we provides specification translation assistant to support future language update, and to provide correct meaning of specification, which also can applicable when
testing for each primitive is unavailable so we cannot decide correct semantics automatically.

@@
